{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-15 paper.tex
WIP on formal decription of uwds

\usepackage{graphicx}
\usepackage{booktabs} % For formal tables

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{booktabs} % For formal tables

@@

\usepackage{amssymb}
\usepackage{amsmath}
\DeclareMathOperator{\transform}{\odot}
\DeclareMathOperator{\filter}{\ominus}
\DeclareMathOperator{\W}{\mathcal{W}}

@@

\subsection{Formal description}

An \uwds \emph{world} $\W^k$ consists in a pair $\{\mathcal{S}^k,
\mathcal{T}^k\}$.

$\mathcal{S}^k=\{N^k, T^k\}$ is a tree representing a spatial
scene (\emph{scene graph}), with $N^k$ the set of nodes and $T^k$ the set of
transformations between the nodes. $|T^k| = |N^k| - 1$ and $n^k_0 \in N^k$ is
called the root node of the scene $\mathcal{S}^k$.

$\mathcal{T}^k=\{Evt^k, Sit^k\}$ is the world's \emph{timeline}, consisting in a
set $Evt^k$ of events (duration-less states) and a set $Sit^k$ of sitations
(states with a start time and an option end time).

\uwds \emph{transformations} $\transform$ are operators that transform one world into
another. They are often unary operator (for instance, $\mathcal{W}^{k'} =
\transform\mathcal{W}^k$), but do not have to. \emph{Filters} (noted $\filter$)
are a common type of unary, antiextensive transformations such as
$\filter\mathcal{W}^k \subseteq \mathcal{W}^k$.

An \uwds \emph{network} $\mathcal{N} = \{W, O\}$ is a directed graph (cycles are
permitted) of worlds $W=\{\mathcal{W}^k\}, k\in0\ldots n$ and operators
$O=\{\transform^l\}, l \in 0\ldots m$.

\begin{tikzpicture}[->,>=stealth',level/.style={sibling distance = 5cm/#1,
    level distance = 1.5cm}] 
    \node {$\mathcal{W}^0$ {\tt\footnotesize base}}
    child{ node  {$\W^1$ {\tt\footnotesize corrected}} edge from parent node[above left] {$\filter$}
            child{ node {$\W^2$ {\tt\footnotesize semantic\_map}} 
                child{ node {}} %for a named pointer
                            child{ node {}}
            }
            child{ node  {$\W^3$ {\tt\footnotesize post\_planning}}
                            child{ node {}}
                            child{ node {}}
            }                            
    }
    ; 
\end{tikzpicture}
